---
title: "Non-Parametric ANCOVA tests for for assess flow state in global cond"
author: Geiser C. Challco <geiser@alumni.usp.br>
comment: Testes Não Parametricos ANCOVA para determinar se houve diferenças significativas
         na aprendizagem (medido usando pre- e pos-testes).
         
         Non-parametric ANCOVA tests to determine whether there were significant differences
         in the learning (measured using pre- and post-tests).
         
         Author - Geiser C. Challco <geiser@alumni.usp.br>
         
         Shiny-Statistic is distributed in the hope that it will be useful,
         but WITHOUT ANY WARRANTY; without even the implied warranty of
         MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
         GNU General Public License for more details.
         
         You should have received a copy of the GNU General Public License.
         If not, see <https://www.gnu.org/licenses/>.
output:
  github_document:
    toc: true
  word_document:
    toc: true
  html_document:
    toc: true
fontsize: 10pt
---


```{r setup, include=FALSE}
# Install and Load Packages
if (!'remotes' %in% rownames(installed.packages())) install.packages('remotes')
if (!"rshinystatistics" %in% rownames(installed.packages())) {
  remotes::install_github("geiser/rshinystatistics")
} else if (packageVersion("rshinystatistics") < "0.0.0.9900") {
  remotes::install_github("geiser/rshinystatistics")
}

wants <- c('ggplot2','ggpubr','rshinystatistics','utils','randomcoloR')
has <- wants %in% rownames(installed.packages())
if (any(!has)) install.packages(wants[!has])

library(readxl)

library(shiny)
library(esquisse)
library(scales)
library(knitr)
library(rmarkdown)

library(utils)
library(ggpubr)
library(ggplot2)
library(randomcoloR)

library(plyr)
library(dplyr)

library(rstatix)
library(rshinystatistics)
```

```{r, include=FALSE, purl=FALSE}
options(knitr.kable.NA = '')
```

# Setting Initial Variables

```{r}
dv = "flow"
dv.pos = "fss"
dv.pre = "dfs"
dv.dif = "dif.flow"

fatores2 <- c("gender","Meaning","Presence","Search")
lfatores2 <- as.list(fatores2)
names(lfatores2) <- fatores2

fatores1 <- c("cond", fatores2)
lfatores1 <- as.list(fatores1)
names(lfatores1) <- fatores1

lfatores <- c(lfatores1)

color <- list()
color[["prepost"]] = c("#ffee65","#f28e2B")
color[["env"]] = c("#a2b6c3","#1054b1","#fc2c8c")
color[["cond"]] = c("#aa8882","#fd7f6f","#42ae20")
color[["gender"]] = c("#FF007F","#4D4DFF")
color[["Meaning"]] = c("#c4ab34","#17cbe1","#f88208")
color[["Presence"]] = c("#c4ab34","#17cbe1","#f88208")
color[["Search"]] = c("#c4ab34","#17cbe1","#f88208")

color[["gender.Meaning"]] = c("#feb1d8","#b1b1fe","#FF007F","#4D4DFF","#dc006d","#3737ff")
color[["gender.Presence"]] = c("#feb1d8","#b1b1fe","#FF007F","#4D4DFF","#dc006d","#3737ff")
color[["gender.Search"]] = c("#feb1d8","#b1b1fe","#FF007F","#4D4DFF","#dc006d","#3737ff")


level <- list()
level[["env"]] = c("neutral","stM","stF")
level[["cond"]] = c("neutral","stThreat","stBoost")
level[["gender"]] = c("F","M")
level[["Meaning"]] = c("lower","median","upper")
level[["Presence"]] = c("lower","median","upper")
level[["Search"]] = c("lower","median","upper")

level[["gender.Meaning"]] = c("F.lower","M.lower","F.median","M.median","F.upper","M.upper")
level[["gender.Presence"]] = c("F.lower","M.lower","F.median","M.median","F.upper","M.upper")
level[["gender.Search"]] = c("F.lower","M.lower","F.median","M.median","F.upper","M.upper")


gdat <- read_excel("../data/data.xlsx", sheet = "results")
gdat <- gdat[!is.na(gdat[[dv.pre]]) & !is.na(gdat[[dv.pos]]),]
if (!dv.dif %in% colnames(gdat))
  gdat[[dv.dif]] <- gdat[[dv.pos]] - gdat[[dv.pre]]





dat <- gdat
dat$cond <- factor(dat[["cond"]], level[["cond"]])
for (coln in c(names(lfatores))) {
  if (length(level[[coln]]) > 0)
    plevel = level[[coln]][level[[coln]] %in% unique(dat[[coln]])]
  else
    plevel = unique(dat[[coln]])[!is.na(unique(dat[[coln]]))]
  
  dat[[coln]] <- factor(dat[[coln]], plevel)
}

dat <- dat[,c("userId", names(lfatores), dv.pre, dv.pos, dv.dif)]

dat.long <- rbind(dat, dat)
dat.long$time <- c(rep("pre", nrow(dat)), rep("pos", nrow(dat)))
dat.long$time <- factor(dat.long$time, c("pre","pos"))
dat.long[[dv]] <- c(dat[[dv.pre]], dat[[dv.pos]])


for (f in c("cond", names(lfatores))) {
  if (is.null(color[[f]]) && length(unique(dat[[f]])) > 0) 
      color[[f]] <- distinctColorPalette(length(unique(dat[[f]])))
}

for (f in c(fatores2)) {
  if (is.null(color[[paste0("cond:",f)]]) && length(unique(dat[[f]])) > 0)
    color[[paste0("cond:",f)]] <- distinctColorPalette(
      length(unique(dat[["cond"]]))*length(unique(dat[[f]])))
}

ldat <- list()
laov <- list()
lpwc <- list()
lemms <- list()
```

# Descriptive Statistics of Initial Data

```{r}
df <- get.descriptives(dat, c(dv.pre, dv.pos, dv.dif), c("cond"),
                       symmetry.test = T, normality.test = F)
df <- plyr::rbind.fill(
  df, do.call(plyr::rbind.fill, lapply(lfatores2, FUN = function(f) {
    if (nrow(dat) > 0 && sum(!is.na(unique(dat[[f]]))) > 1)
      get.descriptives(dat, c(dv.pre,dv.pos), c("cond", f), include.global = F,
                       symmetry.test = T, normality.test = F)
    }))
)
df <- df[,c("variable",fatores1[fatores1 %in% colnames(df)],
            colnames(df)[!colnames(df) %in% c(fatores1,"variable")])]
```


```{r, echo=FALSE, purl=FALSE}
kable(df)
```


# One-way factor analysis for: *flow ~ cond*

```{r}
pdat = remove_group_data(dat[!is.na(dat[["cond"]]),], "dif.flow", "cond", n.limit = 3)

pdat.long <- rbind(pdat[,c("userId","cond")], pdat[,c("userId","cond")])
pdat.long[["time"]] <- c(rep("pre", nrow(pdat)), rep("pos", nrow(pdat)))
pdat.long[["time"]] <- factor(pdat.long[["time"]], c("pre","pos"))
pdat.long[["flow"]] <- c(pdat[["dfs"]], pdat[["fss"]])

y.position.min <- abs(
  max(pdat.long[["flow"]])
  - min(pdat.long[["flow"]]))/20

lvars = as.list(c("dif.flow","fss","dfs"))
names(lvars) = unlist(lvars)
```

## Pre-test and Post-test PairWise comparisons for: *flow ~ cond*

```{r}
pwc.long <- group_by(pdat.long, cond) %>%
  pairwise_wilcox_test(flow ~ time, detailed = T)

df <- pwc.long[,c(".y.","cond","group1","group2","n1","n2","estimate",
                  "statistic","p.adj","p.adj.signif")]
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r, dpi=300, fig.width=12, fig.height=8}
stat.test <- pwc.long %>% add_xy_position(x = "time", fun = "max")
stat.test$y.position <- stat.test$y.position + y.position.min

gg <- ggline(
  pdat.long, x = "time", y = "flow", size = 1.5,
  facet.by = "cond", add = c("mean_ci"), color = "cond",
  position = position_dodge(width = 0.3), palette = color[["cond"]])

pdat.long$xj = jitter(as.numeric(pdat.long[["time"]]), amount=.1)
pdat.long$yj = jitter(pdat.long[["flow"]], amount = .01)

gg + geom_point(
  data = pdat.long, aes_string(x="xj",y="yj", color = "cond"), size=0.5) +
  stat_pvalue_manual(
    stat.test, tip.length = 0, hide.ns = T, label.size = 5,
    position = position_dodge(width = 0.3),
    label = "{ p.adj } ({ p.adj.signif })") + xlab("") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```



## Kruskal and Wilcoxon PairWise comparisons for: *flow ~ cond*


```{r}
kt <- lapply(lvars, FUN = function(x) {
  kruskal_test(pdat, as.formula(paste0(x," ~ cond")))  
})

df <- do.call(rbind.fill, lapply(lvars, function(x) {
  add_significance(merge(
    kt[[x]], kruskal_effsize(pdat, as.formula(paste0(x," ~ cond"))),
    by = c(".y.","n"), suffixes = c("",".ez")))
}))

df <- df[,c(".y.","n","df","statistic","p","p.signif","effsize","magnitude")]
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
pwc <- lapply(lvars, FUN = function(x) {
  pairwise_wilcox_test(pdat, as.formula(paste0(x," ~ cond")), detailed = T)  
})

df <- do.call(rbind.fill, pwc)
```


```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
plots <- lapply(lvars, FUN = function(y) {
  stat.test <- pwc[[y]] %>% add_xy_position(x = "cond")
  stat.test$y.position <- stat.test$y.position + y.position.min
  ggboxplot(pdat, x = "cond", y = y, fill = "cond",
            palette = color[["cond"]]) +
    stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T, label.size = 5,
                       label="{ p.adj } ({ p.adj.signif })") + xlab("")
})
```

```{r, dpi=300, fig.width=16, fig.height=8}
egg::ggarrange(plots[["dfs"]], plots[["fss"]], nrow = 1)
```

```{r, dpi=300, fig.width=8, fig.height=8}
plots[["dif.flow"]] +
  labs(subtitle = get_test_label(kt[["dif.flow"]], detailed = T),
       caption = get_pwc_label(pwc[["dif.flow"]])) +
  ylab("flow (dif)")  +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```




# Two-way factor analysis for: *flow ~ cond:Meaning*


```{r}
pdat = remove_group_data(
  dat[!is.na(dat[["cond"]]) & !is.na(dat[["Meaning"]]),],
  "dif.flow", c("cond","Meaning"), n.limit = 3)

pdat.long <- rbind(pdat[,c("userId","cond","Meaning")],
                   pdat[,c("userId","cond","Meaning")])
pdat.long[["time"]] <- c(rep("pre", nrow(pdat)), rep("pos", nrow(pdat)))
pdat.long[["time"]] <- factor(pdat.long[["time"]], c("pre","pos"))
pdat.long[["flow"]] <- c(pdat[["dfs"]], pdat[["fss"]])

y.position.min <- abs(
  max(pdat.long[["flow"]])
  - min(pdat.long[["flow"]]))/20

lvars = as.list(c("dif.flow","fss","dfs"))
names(lvars) = unlist(lvars)
```

## Pre-test and Post-test PairWise comparisons for: *flow ~ cond:Meaning*

```{r}
pwc.long <- group_by(pdat.long, cond:Meaning) %>%
  pairwise_wilcox_test(flow ~ time, detailed = T)

df <- pwc.long[,c(".y.","cond:Meaning","group1","group2","n1","n2","estimate",
                  "statistic","p.adj","p.adj.signif")]
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r, dpi=300, fig.width=12, fig.height=8}
pwc.long <- group_by(pdat.long, cond, Meaning) %>%
  pairwise_wilcox_test(flow ~ time, detailed = T)

stat.test <- pwc.long %>% add_xy_position(x = "time", fun = "mean_ci")
sidx = which(stat.test$p.adj.signif != "ns")
stat.test$y.position[sidx] <- stat.test$y.position[sidx] + y.position.min * (1:length(sidx))

gg <- ggline(
  pdat.long, x = "time", y = "flow",
  color = "Meaning", linetype = "Meaning", shape = "Meaning", size = 1.5,
  facet.by = "cond", add = c("mean_ci"),
  position = position_dodge(width = 0.3), palette = color[["Meaning"]])

pdat.long$xj = jitter(as.numeric(pdat.long[["time"]]), amount=.1)
pdat.long$yj = jitter(pdat.long[["flow"]], amount = .01)

gg + geom_point(
  data = pdat.long, aes_string(x="xj",y="yj",colour="Meaning"), size=0.5) +
  stat_pvalue_manual(
    stat.test, tip.length = 0, hide.ns = T, label.size = 5,
    position = position_dodge(width = 0.3), color = "Meaning",
    label = "{ p.adj } ({ p.adj.signif })") + xlab("") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```

## Scheirer and Wilcoxon PairWise comparisons for: *flow ~ cond:Meaning*


```{r}
sch <- lapply(lvars, FUN = function(x) {
  scheirer.test(pdat, x, c("cond","Meaning"), as.table = T) 
})
df <- do.call(rbind.fill, sch)
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
pwc <- lapply(lvars, FUN = function(x) {
  list(
    cond = tryCatch(pairwise_wilcox_test(group_by(pdat, Meaning),
                                 as.formula(paste0(x," ~ cond")), detailed = T)
                         , error = function(e) NULL),
    Meaning = tryCatch(pairwise_wilcox_test(group_by(pdat, cond),
                                 as.formula(paste0(x," ~ Meaning")), detailed = T)
                         , error = function(e) NULL)
  )
})

df <- do.call(rbind.fill, lapply(pwc, FUN =  function(x) {
  do.call(rbind.fill, x)
}))

ivs = c()
if ("cond" %in% colnames(df)) ivs = c(ivs, "cond")
if ("Meaning" %in% colnames(df)) ivs = c(ivs, "Meaning")
df <- df[,c(".y.",ivs,"group1","group2","n1","n2","estimate",
            "statistic","p.adj","p.adj.signif")]
```


```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
plots <- lapply(lvars, FUN = function(y) {
  livs = list("cond", "Meaning")
  names(livs) = unlist(livs)
  lapply(livs, FUN = function(x) {
    iv2 = setdiff(names(livs), x)
    if (!is.null(pwc[[y]][[iv2]])) {
      stat.test <- pwc[[y]][[iv2]] %>% add_xy_position(x = x, fun = "max")
      sidx = which(stat.test$p.adj.signif != "ns")
      stat.test$y.position[sidx] <- stat.test$y.position[sidx] + y.position.min * (1:length(sidx))
      
      ggboxplot(pdat, x = x, y = y, fill = iv2, palette = color[[iv2]]) +
        stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T, label.size = 5,
                           label="{ p.adj } ({ p.adj.signif })") + xlab("")
    }
  })
})
```

```{r, dpi=300, fig.width=16, fig.height=8}
if (!is.null(plots[["dfs"]][["cond"]]) &&
    !is.null(plots[["fss"]][["cond"]])) {
  egg::ggarrange(plots[["dfs"]][["cond"]],
                 plots[["fss"]][["cond"]], nrow = 1)  
}
```


```{r, dpi=300, fig.width=16, fig.height=8}
if (!is.null(plots[["dfs"]][["Meaning"]]) &&
    !is.null(plots[["fss"]][["Meaning"]])) {
  egg::ggarrange(plots[["dfs"]][["Meaning"]],
                 plots[["fss"]][["Meaning"]], nrow = 1)
}
```

```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["dif.flow"]]
idx = which(psch$Effect == "cond:Meaning") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["dif.flow"]][["cond"]]))
  plots[["dif.flow"]][["cond"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["dif.flow"]][["Meaning"]])) +
    ylab("flow (dif)") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```


```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["dif.flow"]]
idx = which(psch$Effect == "cond:Meaning") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["dif.flow"]][["Meaning"]]))
  plots[["dif.flow"]][["Meaning"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["dif.flow"]][["cond"]])) +
    ylab("flow (dif)") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```






# Two-way factor analysis for: *flow ~ cond:Presence*


```{r}
pdat = remove_group_data(
  dat[!is.na(dat[["cond"]]) & !is.na(dat[["Presence"]]),],
  "dif.flow", c("cond","Presence"), n.limit = 3)

pdat.long <- rbind(pdat[,c("userId","cond","Presence")],
                   pdat[,c("userId","cond","Presence")])
pdat.long[["time"]] <- c(rep("pre", nrow(pdat)), rep("pos", nrow(pdat)))
pdat.long[["time"]] <- factor(pdat.long[["time"]], c("pre","pos"))
pdat.long[["flow"]] <- c(pdat[["dfs"]], pdat[["fss"]])

y.position.min <- abs(
  max(pdat.long[["flow"]])
  - min(pdat.long[["flow"]]))/20

lvars = as.list(c("dif.flow","fss","dfs"))
names(lvars) = unlist(lvars)
```

## Pre-test and Post-test PairWise comparisons for: *flow ~ cond:Presence*

```{r}
pwc.long <- group_by(pdat.long, cond:Presence) %>%
  pairwise_wilcox_test(flow ~ time, detailed = T)

df <- pwc.long[,c(".y.","cond:Presence","group1","group2","n1","n2","estimate",
                  "statistic","p.adj","p.adj.signif")]
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r, dpi=300, fig.width=12, fig.height=8}
pwc.long <- group_by(pdat.long, cond, Presence) %>%
  pairwise_wilcox_test(flow ~ time, detailed = T)

stat.test <- pwc.long %>% add_xy_position(x = "time", fun = "mean_ci")
sidx = which(stat.test$p.adj.signif != "ns")
stat.test$y.position[sidx] <- stat.test$y.position[sidx] + y.position.min * (1:length(sidx))

gg <- ggline(
  pdat.long, x = "time", y = "flow",
  color = "Presence", linetype = "Presence", shape = "Presence", size = 1.5,
  facet.by = "cond", add = c("mean_ci"),
  position = position_dodge(width = 0.3), palette = color[["Presence"]])

pdat.long$xj = jitter(as.numeric(pdat.long[["time"]]), amount=.1)
pdat.long$yj = jitter(pdat.long[["flow"]], amount = .01)

gg + geom_point(
  data = pdat.long, aes_string(x="xj",y="yj",colour="Presence"), size=0.5) +
  stat_pvalue_manual(
    stat.test, tip.length = 0, hide.ns = T, label.size = 5,
    position = position_dodge(width = 0.3), color = "Presence",
    label = "{ p.adj } ({ p.adj.signif })") + xlab("") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```

## Scheirer and Wilcoxon PairWise comparisons for: *flow ~ cond:Presence*


```{r}
sch <- lapply(lvars, FUN = function(x) {
  scheirer.test(pdat, x, c("cond","Presence"), as.table = T) 
})
df <- do.call(rbind.fill, sch)
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
pwc <- lapply(lvars, FUN = function(x) {
  list(
    cond = tryCatch(pairwise_wilcox_test(group_by(pdat, Presence),
                                 as.formula(paste0(x," ~ cond")), detailed = T)
                         , error = function(e) NULL),
    Presence = tryCatch(pairwise_wilcox_test(group_by(pdat, cond),
                                 as.formula(paste0(x," ~ Presence")), detailed = T)
                         , error = function(e) NULL)
  )
})

df <- do.call(rbind.fill, lapply(pwc, FUN =  function(x) {
  do.call(rbind.fill, x)
}))

ivs = c()
if ("cond" %in% colnames(df)) ivs = c(ivs, "cond")
if ("Presence" %in% colnames(df)) ivs = c(ivs, "Presence")
df <- df[,c(".y.",ivs,"group1","group2","n1","n2","estimate",
            "statistic","p.adj","p.adj.signif")]
```


```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
plots <- lapply(lvars, FUN = function(y) {
  livs = list("cond", "Presence")
  names(livs) = unlist(livs)
  lapply(livs, FUN = function(x) {
    iv2 = setdiff(names(livs), x)
    if (!is.null(pwc[[y]][[iv2]])) {
      stat.test <- pwc[[y]][[iv2]] %>% add_xy_position(x = x, fun = "max")
      sidx = which(stat.test$p.adj.signif != "ns")
      stat.test$y.position[sidx] <- stat.test$y.position[sidx] + y.position.min * (1:length(sidx))
      
      ggboxplot(pdat, x = x, y = y, fill = iv2, palette = color[[iv2]]) +
        stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T, label.size = 5,
                           label="{ p.adj } ({ p.adj.signif })") + xlab("")
    }
  })
})
```

```{r, dpi=300, fig.width=16, fig.height=8}
if (!is.null(plots[["dfs"]][["cond"]]) &&
    !is.null(plots[["fss"]][["cond"]])) {
  egg::ggarrange(plots[["dfs"]][["cond"]],
                 plots[["fss"]][["cond"]], nrow = 1)  
}
```


```{r, dpi=300, fig.width=16, fig.height=8}
if (!is.null(plots[["dfs"]][["Presence"]]) &&
    !is.null(plots[["fss"]][["Presence"]])) {
  egg::ggarrange(plots[["dfs"]][["Presence"]],
                 plots[["fss"]][["Presence"]], nrow = 1)
}
```

```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["dif.flow"]]
idx = which(psch$Effect == "cond:Presence") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["dif.flow"]][["cond"]]))
  plots[["dif.flow"]][["cond"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["dif.flow"]][["Presence"]])) +
    ylab("flow (dif)") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```


```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["dif.flow"]]
idx = which(psch$Effect == "cond:Presence") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["dif.flow"]][["Presence"]]))
  plots[["dif.flow"]][["Presence"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["dif.flow"]][["cond"]])) +
    ylab("flow (dif)") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```






# Two-way factor analysis for: *flow ~ cond:Search*


```{r}
pdat = remove_group_data(
  dat[!is.na(dat[["cond"]]) & !is.na(dat[["Search"]]),],
  "dif.flow", c("cond","Search"), n.limit = 3)

pdat.long <- rbind(pdat[,c("userId","cond","Search")],
                   pdat[,c("userId","cond","Search")])
pdat.long[["time"]] <- c(rep("pre", nrow(pdat)), rep("pos", nrow(pdat)))
pdat.long[["time"]] <- factor(pdat.long[["time"]], c("pre","pos"))
pdat.long[["flow"]] <- c(pdat[["dfs"]], pdat[["fss"]])

y.position.min <- abs(
  max(pdat.long[["flow"]])
  - min(pdat.long[["flow"]]))/20

lvars = as.list(c("dif.flow","fss","dfs"))
names(lvars) = unlist(lvars)
```

## Pre-test and Post-test PairWise comparisons for: *flow ~ cond:Search*

```{r}
pwc.long <- group_by(pdat.long, cond:Search) %>%
  pairwise_wilcox_test(flow ~ time, detailed = T)

df <- pwc.long[,c(".y.","cond:Search","group1","group2","n1","n2","estimate",
                  "statistic","p.adj","p.adj.signif")]
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r, dpi=300, fig.width=12, fig.height=8}
pwc.long <- group_by(pdat.long, cond, Search) %>%
  pairwise_wilcox_test(flow ~ time, detailed = T)

stat.test <- pwc.long %>% add_xy_position(x = "time", fun = "mean_ci")
sidx = which(stat.test$p.adj.signif != "ns")
stat.test$y.position[sidx] <- stat.test$y.position[sidx] + y.position.min * (1:length(sidx))

gg <- ggline(
  pdat.long, x = "time", y = "flow",
  color = "Search", linetype = "Search", shape = "Search", size = 1.5,
  facet.by = "cond", add = c("mean_ci"),
  position = position_dodge(width = 0.3), palette = color[["Search"]])

pdat.long$xj = jitter(as.numeric(pdat.long[["time"]]), amount=.1)
pdat.long$yj = jitter(pdat.long[["flow"]], amount = .01)

gg + geom_point(
  data = pdat.long, aes_string(x="xj",y="yj",colour="Search"), size=0.5) +
  stat_pvalue_manual(
    stat.test, tip.length = 0, hide.ns = T, label.size = 5,
    position = position_dodge(width = 0.3), color = "Search",
    label = "{ p.adj } ({ p.adj.signif })") + xlab("") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```

## Scheirer and Wilcoxon PairWise comparisons for: *flow ~ cond:Search*


```{r}
sch <- lapply(lvars, FUN = function(x) {
  scheirer.test(pdat, x, c("cond","Search"), as.table = T) 
})
df <- do.call(rbind.fill, sch)
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
pwc <- lapply(lvars, FUN = function(x) {
  list(
    cond = tryCatch(pairwise_wilcox_test(group_by(pdat, Search),
                                 as.formula(paste0(x," ~ cond")), detailed = T)
                         , error = function(e) NULL),
    Search = tryCatch(pairwise_wilcox_test(group_by(pdat, cond),
                                 as.formula(paste0(x," ~ Search")), detailed = T)
                         , error = function(e) NULL)
  )
})

df <- do.call(rbind.fill, lapply(pwc, FUN =  function(x) {
  do.call(rbind.fill, x)
}))

ivs = c()
if ("cond" %in% colnames(df)) ivs = c(ivs, "cond")
if ("Search" %in% colnames(df)) ivs = c(ivs, "Search")
df <- df[,c(".y.",ivs,"group1","group2","n1","n2","estimate",
            "statistic","p.adj","p.adj.signif")]
```


```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
plots <- lapply(lvars, FUN = function(y) {
  livs = list("cond", "Search")
  names(livs) = unlist(livs)
  lapply(livs, FUN = function(x) {
    iv2 = setdiff(names(livs), x)
    if (!is.null(pwc[[y]][[iv2]])) {
      stat.test <- pwc[[y]][[iv2]] %>% add_xy_position(x = x, fun = "max")
      sidx = which(stat.test$p.adj.signif != "ns")
      stat.test$y.position[sidx] <- stat.test$y.position[sidx] + y.position.min * (1:length(sidx))
      
      ggboxplot(pdat, x = x, y = y, fill = iv2, palette = color[[iv2]]) +
        stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T, label.size = 5,
                           label="{ p.adj } ({ p.adj.signif })") + xlab("")
    }
  })
})
```

```{r, dpi=300, fig.width=16, fig.height=8}
if (!is.null(plots[["dfs"]][["cond"]]) &&
    !is.null(plots[["fss"]][["cond"]])) {
  egg::ggarrange(plots[["dfs"]][["cond"]],
                 plots[["fss"]][["cond"]], nrow = 1)  
}
```


```{r, dpi=300, fig.width=16, fig.height=8}
if (!is.null(plots[["dfs"]][["Search"]]) &&
    !is.null(plots[["fss"]][["Search"]])) {
  egg::ggarrange(plots[["dfs"]][["Search"]],
                 plots[["fss"]][["Search"]], nrow = 1)
}
```

```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["dif.flow"]]
idx = which(psch$Effect == "cond:Search") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["dif.flow"]][["cond"]]))
  plots[["dif.flow"]][["cond"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["dif.flow"]][["Search"]])) +
    ylab("flow (dif)") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```


```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["dif.flow"]]
idx = which(psch$Effect == "cond:Search") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["dif.flow"]][["Search"]]))
  plots[["dif.flow"]][["Search"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["dif.flow"]][["cond"]])) +
    ylab("flow (dif)") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```





