---
title: "Non-Parametric ANOVA tests for for assess correct.answers based on environment and gender"
author: Geiser C. Challco <geiser@alumni.usp.br>
comment: Testes Não Parametricos ANCOVA para determinar se houve diferenças significativas
         na aprendizagem (medido usando pre- e pos-testes).
         
         Non-parametric ANCOVA tests to determine whether there were significant differences
         in the learning (measured using pre- and post-tests).
         
         Author - Geiser C. Challco <geiser@alumni.usp.br>
         
         Shiny-Statistic is distributed in the hope that it will be useful,
         but WITHOUT ANY WARRANTY; without even the implied warranty of
         MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
         GNU General Public License for more details.
         
         You should have received a copy of the GNU General Public License.
         If not, see <https://www.gnu.org/licenses/>.
output:
  github_document:
    toc: true
  word_document:
    toc: true
  html_document:
    toc: true
fontsize: 10pt
---


```{r setup, include=FALSE}
# Install and Load Packages
if (!'remotes' %in% rownames(installed.packages())) install.packages('remotes')
if (!"rshinystatistics" %in% rownames(installed.packages())) {
  remotes::install_github("geiser/rshinystatistics")
} else if (packageVersion("rshinystatistics") < "0.0.0.9900") {
  remotes::install_github("geiser/rshinystatistics")
}

wants <- c('ggplot2','ggpubr','rshinystatistics','utils','randomcoloR')
has <- wants %in% rownames(installed.packages())
if (any(!has)) install.packages(wants[!has])

library(readxl)

library(shiny)
library(esquisse)
library(scales)
library(knitr)
library(rmarkdown)

library(utils)
library(ggpubr)
library(ggplot2)
library(randomcoloR)

library(plyr)
library(dplyr)

library(rstatix)
library(rshinystatistics)
```

```{r, include=FALSE, purl=FALSE}
options(knitr.kable.NA = '')
```

# Setting Initial Variables

```{r}
dv = "correct.answers"

fatores2 <- c("gender","gender.Meaning","gender.Presence","gender.Search")
lfatores2 <- as.list(fatores2)
names(lfatores2) <- fatores2

fatores1 <- c("env", fatores2)
lfatores1 <- as.list(fatores1)
names(lfatores1) <- fatores1

lfatores <- c(lfatores1)

color <- list()
color[["env"]] = c("#a2b6c3","#1054b1","#fc2c8c")
color[["cond"]] = c("#aa8882","#fd7f6f","#42ae20")
color[["cond.env"]] = c("#aa8882","#fd7f6f","#42ae20")
color[["gender"]] = c("#FF007F","#4D4DFF")
color[["Meaning"]] = c("#c4ab34","#17cbe1","#f88208")
color[["Presence"]] = c("#c4ab34","#17cbe1","#f88208")
color[["Search"]] = c("#c4ab34","#17cbe1","#f88208")

color[["gender.Meaning"]] = c("#feb1d8","#b1b1fe","#FF007F","#4D4DFF","#dc006d","#3737ff")
color[["gender.Presence"]] = c("#feb1d8","#b1b1fe","#FF007F","#4D4DFF","#dc006d","#3737ff")
color[["gender.Search"]] = c("#feb1d8","#b1b1fe","#FF007F","#4D4DFF","#dc006d","#3737ff")


level <- list()
level[["env"]] = c("neutral","stM","stF")
level[["cond"]] = c("neutral","stThreat","stBoost")
level[["cond.env"]] = c("neutral","stThreat","stBoost")
level[["gender"]] = c("F","M")
level[["Meaning"]] = c("lower","median","upper")
level[["Presence"]] = c("lower","median","upper")
level[["Search"]] = c("lower","median","upper")

level[["gender.Meaning"]] = c("F.lower","M.lower","F.median","M.median","F.upper","M.upper")
level[["gender.Presence"]] = c("F.lower","M.lower","F.median","M.median","F.upper","M.upper")
level[["gender.Search"]] = c("F.lower","M.lower","F.median","M.median","F.upper","M.upper")


gdat <- read_excel("../data/data.xlsx", sheet = "results")
gdat <- gdat[!is.na(gdat[[dv]]),]




dat <- gdat
dat$env <- factor(dat[["env"]], level[["env"]])
for (coln in c(names(lfatores))) {
  if (length(level[[coln]]) > 0)
    plevel = level[[coln]][level[[coln]] %in% unique(dat[[coln]])]
  else
    plevel = unique(dat[[coln]])[!is.na(unique(dat[[coln]]))]
  
  dat[[coln]] <- factor(dat[[coln]], plevel)
}

dat <- dat[,c("userId", names(lfatores), dv)]

for (f in c("env", names(lfatores))) {
  if (is.null(color[[f]]) && length(unique(dat[[f]])) > 0) 
      color[[f]] <- distinctColorPalette(length(unique(dat[[f]])))
}

for (f in c(fatores2)) {
  if (is.null(color[[paste0("env:",f)]]) && length(unique(dat[[f]])) > 0)
    color[[paste0("env:",f)]] <- distinctColorPalette(
      length(unique(dat[["env"]]))*length(unique(dat[[f]])))
}

ldat <- list()
laov <- list()
lpwc <- list()
lemms <- list()
```

# Descriptive Statistics of Initial Data

```{r}
df <- get.descriptives(dat, c(dv), c("env"),
                       symmetry.test = T, normality.test = F)
df <- plyr::rbind.fill(
  df, do.call(plyr::rbind.fill, lapply(lfatores2, FUN = function(f) {
    if (nrow(dat) > 0 && sum(!is.na(unique(dat[[f]]))) > 1)
      get.descriptives(dat, c(dv), c("env", f), include.global = F,
                       symmetry.test = T, normality.test = F)
    }))
)
df <- df[,c("variable",fatores1[fatores1 %in% colnames(df)],
            colnames(df)[!colnames(df) %in% c(fatores1,"variable")])]
```


```{r, echo=FALSE, purl=FALSE}
kable(df)
```


# One-way factor analysis for: *dv ~ env*

```{r}
pdat = remove_group_data(dat[!is.na(dat[["env"]]),], "correct.answers", "env", n.limit = 3)

y.position.min <- abs(
  max(pdat[["correct.answers"]])
  - min(pdat[["correct.answers"]]))/20

lvars = as.list(c("correct.answers"))
names(lvars) = unlist(lvars)
```

## Kruskal and Wilcoxon PairWise comparisons for: *correct.answers ~ env*


```{r}
kt <- lapply(lvars, FUN = function(x) {
  kruskal_test(pdat, as.formula(paste0(x," ~ env")))  
})

df <- do.call(rbind.fill, lapply(lvars, function(x) {
  add_significance(merge(
    kt[[x]], kruskal_effsize(pdat, as.formula(paste0(x," ~ env"))),
    by = c(".y.","n"), suffixes = c("",".ez")))
}))

df <- df[,c(".y.","n","df","statistic","p","p.signif","effsize","magnitude")]
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
pwc <- lapply(lvars, FUN = function(x) {
  pairwise_wilcox_test(pdat, as.formula(paste0(x," ~ env")), detailed = T)  
})

df <- do.call(rbind.fill, pwc)
```


```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
plots <- lapply(lvars, FUN = function(y) {
  stat.test <- pwc[[y]] %>% add_xy_position(x = "env")
  stat.test$y.position <- stat.test$y.position + y.position.min
  ggboxplot(pdat, x = "env", y = y, fill = "env",
            palette = color[["env"]]) +
    stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T, label.size = 5,
                       label="{ p.adj } ({ p.adj.signif })") + xlab("")
})
```


```{r, dpi=300, fig.width=8, fig.height=8}
plots[["correct.answers"]] +
  labs(subtitle = get_test_label(kt[["correct.answers"]], detailed = T),
       caption = get_pwc_label(pwc[["correct.answers"]])) +
  ylab("correct.answers")  +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```


# Two-way factor analysis for: *dv ~ env:gender*


```{r}
pdat = remove_group_data(
  dat[!is.na(dat[["env"]]) & !is.na(dat[["gender"]]),],
  "correct.answers", c("env","gender"), n.limit = 3)

y.position.min <- abs(max(pdat[["correct.answers"]]) - min(pdat[["correct.answers"]]))/20

lvars = as.list(c("correct.answers"))
names(lvars) = unlist(lvars)
```

## Scheirer and Wilcoxon PairWise comparisons for: *correct.answers ~ env:gender*


```{r}
sch <- lapply(lvars, FUN = function(x) {
  scheirer.test(pdat, x, c("env","gender"), as.table = T) 
})
df <- do.call(rbind.fill, sch)
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
pwc <- lapply(lvars, FUN = function(x) {
  list(
    env = tryCatch(pairwise_wilcox_test(group_by(pdat, gender),
                                 as.formula(paste0(x," ~ env")), detailed = T)
                         , error = function(e) NULL),
    gender = tryCatch(pairwise_wilcox_test(group_by(pdat, env),
                                 as.formula(paste0(x," ~ gender")), detailed = T)
                         , error = function(e) NULL)
  )
})

df <- do.call(rbind.fill, lapply(pwc, FUN =  function(x) {
  do.call(rbind.fill, x)
}))

ivs = c()
if ("env" %in% colnames(df)) ivs = c(ivs, "env")
if ("gender" %in% colnames(df)) ivs = c(ivs, "gender")
df <- df[,c(".y.",ivs,"group1","group2","n1","n2","estimate",
            "statistic","p.adj","p.adj.signif")]
```


```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
plots <- lapply(lvars, FUN = function(y) {
  livs = list("env", "gender")
  names(livs) = unlist(livs)
  lapply(livs, FUN = function(x) {
    iv2 = setdiff(names(livs), x)
    if (!is.null(pwc[[y]][[iv2]])) {
      stat.test <- pwc[[y]][[iv2]] %>% add_xy_position(x = x, fun = "max")
      sidx = which(stat.test$p.adj.signif != "ns")
      stat.test$y.position[sidx] <- stat.test$y.position[sidx] + y.position.min * (1:length(sidx))
      
      ggboxplot(pdat, x = x, y = y, fill = iv2, palette = color[[iv2]]) +
        stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T, label.size = 5,
                           label="{ p.adj } ({ p.adj.signif })") + xlab("")
    }
  })
})
```


```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["correct.answers"]]
idx = which(psch$Effect == "env:gender") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["correct.answers"]][["env"]]))
  plots[["correct.answers"]][["env"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["correct.answers"]][["gender"]])) +
    ylab("correct.answers") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```


```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["correct.answers"]]
idx = which(psch$Effect == "env:gender") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["correct.answers"]][["gender"]]))
  plots[["correct.answers"]][["gender"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["correct.answers"]][["env"]])) +
    ylab("correct.answers") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```






# Two-way factor analysis for: *dv ~ env:gender.Meaning*


```{r}
pdat = remove_group_data(
  dat[!is.na(dat[["env"]]) & !is.na(dat[["gender.Meaning"]]),],
  "correct.answers", c("env","gender.Meaning"), n.limit = 3)

y.position.min <- abs(max(pdat[["correct.answers"]]) - min(pdat[["correct.answers"]]))/20

lvars = as.list(c("correct.answers"))
names(lvars) = unlist(lvars)
```

## Scheirer and Wilcoxon PairWise comparisons for: *correct.answers ~ env:gender.Meaning*


```{r}
sch <- lapply(lvars, FUN = function(x) {
  scheirer.test(pdat, x, c("env","gender.Meaning"), as.table = T) 
})
df <- do.call(rbind.fill, sch)
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
pwc <- lapply(lvars, FUN = function(x) {
  list(
    env = tryCatch(pairwise_wilcox_test(group_by(pdat, gender.Meaning),
                                 as.formula(paste0(x," ~ env")), detailed = T)
                         , error = function(e) NULL),
    gender.Meaning = tryCatch(pairwise_wilcox_test(group_by(pdat, env),
                                 as.formula(paste0(x," ~ gender.Meaning")), detailed = T)
                         , error = function(e) NULL)
  )
})

df <- do.call(rbind.fill, lapply(pwc, FUN =  function(x) {
  do.call(rbind.fill, x)
}))

ivs = c()
if ("env" %in% colnames(df)) ivs = c(ivs, "env")
if ("gender.Meaning" %in% colnames(df)) ivs = c(ivs, "gender.Meaning")
df <- df[,c(".y.",ivs,"group1","group2","n1","n2","estimate",
            "statistic","p.adj","p.adj.signif")]
```


```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
plots <- lapply(lvars, FUN = function(y) {
  livs = list("env", "gender.Meaning")
  names(livs) = unlist(livs)
  lapply(livs, FUN = function(x) {
    iv2 = setdiff(names(livs), x)
    if (!is.null(pwc[[y]][[iv2]])) {
      stat.test <- pwc[[y]][[iv2]] %>% add_xy_position(x = x, fun = "max")
      sidx = which(stat.test$p.adj.signif != "ns")
      stat.test$y.position[sidx] <- stat.test$y.position[sidx] + y.position.min * (1:length(sidx))
      
      ggboxplot(pdat, x = x, y = y, fill = iv2, palette = color[[iv2]]) +
        stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T, label.size = 5,
                           label="{ p.adj } ({ p.adj.signif })") + xlab("")
    }
  })
})
```


```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["correct.answers"]]
idx = which(psch$Effect == "env:gender.Meaning") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["correct.answers"]][["env"]]))
  plots[["correct.answers"]][["env"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["correct.answers"]][["gender.Meaning"]])) +
    ylab("correct.answers") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```


```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["correct.answers"]]
idx = which(psch$Effect == "env:gender.Meaning") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["correct.answers"]][["gender.Meaning"]]))
  plots[["correct.answers"]][["gender.Meaning"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["correct.answers"]][["env"]])) +
    ylab("correct.answers") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```






# Two-way factor analysis for: *dv ~ env:gender.Presence*


```{r}
pdat = remove_group_data(
  dat[!is.na(dat[["env"]]) & !is.na(dat[["gender.Presence"]]),],
  "correct.answers", c("env","gender.Presence"), n.limit = 3)

y.position.min <- abs(max(pdat[["correct.answers"]]) - min(pdat[["correct.answers"]]))/20

lvars = as.list(c("correct.answers"))
names(lvars) = unlist(lvars)
```

## Scheirer and Wilcoxon PairWise comparisons for: *correct.answers ~ env:gender.Presence*


```{r}
sch <- lapply(lvars, FUN = function(x) {
  scheirer.test(pdat, x, c("env","gender.Presence"), as.table = T) 
})
df <- do.call(rbind.fill, sch)
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
pwc <- lapply(lvars, FUN = function(x) {
  list(
    env = tryCatch(pairwise_wilcox_test(group_by(pdat, gender.Presence),
                                 as.formula(paste0(x," ~ env")), detailed = T)
                         , error = function(e) NULL),
    gender.Presence = tryCatch(pairwise_wilcox_test(group_by(pdat, env),
                                 as.formula(paste0(x," ~ gender.Presence")), detailed = T)
                         , error = function(e) NULL)
  )
})

df <- do.call(rbind.fill, lapply(pwc, FUN =  function(x) {
  do.call(rbind.fill, x)
}))

ivs = c()
if ("env" %in% colnames(df)) ivs = c(ivs, "env")
if ("gender.Presence" %in% colnames(df)) ivs = c(ivs, "gender.Presence")
df <- df[,c(".y.",ivs,"group1","group2","n1","n2","estimate",
            "statistic","p.adj","p.adj.signif")]
```


```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
plots <- lapply(lvars, FUN = function(y) {
  livs = list("env", "gender.Presence")
  names(livs) = unlist(livs)
  lapply(livs, FUN = function(x) {
    iv2 = setdiff(names(livs), x)
    if (!is.null(pwc[[y]][[iv2]])) {
      stat.test <- pwc[[y]][[iv2]] %>% add_xy_position(x = x, fun = "max")
      sidx = which(stat.test$p.adj.signif != "ns")
      stat.test$y.position[sidx] <- stat.test$y.position[sidx] + y.position.min * (1:length(sidx))
      
      ggboxplot(pdat, x = x, y = y, fill = iv2, palette = color[[iv2]]) +
        stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T, label.size = 5,
                           label="{ p.adj } ({ p.adj.signif })") + xlab("")
    }
  })
})
```


```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["correct.answers"]]
idx = which(psch$Effect == "env:gender.Presence") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["correct.answers"]][["env"]]))
  plots[["correct.answers"]][["env"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["correct.answers"]][["gender.Presence"]])) +
    ylab("correct.answers") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```


```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["correct.answers"]]
idx = which(psch$Effect == "env:gender.Presence") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["correct.answers"]][["gender.Presence"]]))
  plots[["correct.answers"]][["gender.Presence"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["correct.answers"]][["env"]])) +
    ylab("correct.answers") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```






# Two-way factor analysis for: *dv ~ env:gender.Search*


```{r}
pdat = remove_group_data(
  dat[!is.na(dat[["env"]]) & !is.na(dat[["gender.Search"]]),],
  "correct.answers", c("env","gender.Search"), n.limit = 3)

y.position.min <- abs(max(pdat[["correct.answers"]]) - min(pdat[["correct.answers"]]))/20

lvars = as.list(c("correct.answers"))
names(lvars) = unlist(lvars)
```

## Scheirer and Wilcoxon PairWise comparisons for: *correct.answers ~ env:gender.Search*


```{r}
sch <- lapply(lvars, FUN = function(x) {
  scheirer.test(pdat, x, c("env","gender.Search"), as.table = T) 
})
df <- do.call(rbind.fill, sch)
```

```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
pwc <- lapply(lvars, FUN = function(x) {
  list(
    env = tryCatch(pairwise_wilcox_test(group_by(pdat, gender.Search),
                                 as.formula(paste0(x," ~ env")), detailed = T)
                         , error = function(e) NULL),
    gender.Search = tryCatch(pairwise_wilcox_test(group_by(pdat, env),
                                 as.formula(paste0(x," ~ gender.Search")), detailed = T)
                         , error = function(e) NULL)
  )
})

df <- do.call(rbind.fill, lapply(pwc, FUN =  function(x) {
  do.call(rbind.fill, x)
}))

ivs = c()
if ("env" %in% colnames(df)) ivs = c(ivs, "env")
if ("gender.Search" %in% colnames(df)) ivs = c(ivs, "gender.Search")
df <- df[,c(".y.",ivs,"group1","group2","n1","n2","estimate",
            "statistic","p.adj","p.adj.signif")]
```


```{r, echo=FALSE, purl=FALSE}
kable(df)
```


```{r}
plots <- lapply(lvars, FUN = function(y) {
  livs = list("env", "gender.Search")
  names(livs) = unlist(livs)
  lapply(livs, FUN = function(x) {
    iv2 = setdiff(names(livs), x)
    if (!is.null(pwc[[y]][[iv2]])) {
      stat.test <- pwc[[y]][[iv2]] %>% add_xy_position(x = x, fun = "max")
      sidx = which(stat.test$p.adj.signif != "ns")
      stat.test$y.position[sidx] <- stat.test$y.position[sidx] + y.position.min * (1:length(sidx))
      
      ggboxplot(pdat, x = x, y = y, fill = iv2, palette = color[[iv2]]) +
        stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T, label.size = 5,
                           label="{ p.adj } ({ p.adj.signif })") + xlab("")
    }
  })
})
```


```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["correct.answers"]]
idx = which(psch$Effect == "env:gender.Search") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["correct.answers"]][["env"]]))
  plots[["correct.answers"]][["env"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["correct.answers"]][["gender.Search"]])) +
    ylab("correct.answers") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```


```{r, dpi=300, fig.width=8, fig.height=8}
psch = sch[["correct.answers"]]
idx = which(psch$Effect == "env:gender.Search") 

dof = floor(as.double(psch$Df[idx]))
dof.res = floor(as.double(psch$Df[which(psch$Effect == "Residuals")]))
statistic = round(as.double(psch$H[idx]), 3)
p = round(as.double(psch[["p.value"]][idx]), 3)
pval = ifelse(p < 0.001,paste0(" , p<0.001"),paste0(" , p=",p))

if (!is.null(plots[["correct.answers"]][["gender.Search"]]))
  plots[["correct.answers"]][["gender.Search"]] +
    labs(subtitle = paste0("Scheirer-Ray-Hare H(", dof, ",", 
          dof.res, ")=", statistic, pval),
         caption = get_pwc_label(pwc[["correct.answers"]][["env"]])) +
    ylab("correct.answers") +
  theme(strip.text = element_text(size = 16),
        axis.text = element_text(size = 18))
```





